Mr.\ Oshiro wants to build a new hotel in Celeste Mountain Range.
He needs you to find a good place him. 
First, Oshiro wants to build the hotel on a continuous segment 
without any valley in between,
and the hotel should be as wide as possible. 
However, some places are too dangerous for the construction, 
so he will ask you this question several times: 
what is the maximum width of a constructible hotel 
in a certain segment of Celeste Mountain Range?

To clarify the problem statement, we define the following terms.
\begin{itemize}
\item Celeste Mountain Range is $n$ kilometers long.
\item The topography (shape of the land surface) is described by an 
      integer sequence $h_0,\dots,h_{n-1}$ indicating the average heights in 
      meters. $h_i$ is the average height in the area from the $i$-th kilometer
      to the $(i+1)$-th kilometer of Celeste Mountain Range. 
\item Every query will be a continuous segment in Celeste Mountain Range
      that has corresponding sequence of heights.
\item A valley is a place which is lower than its neighbors. In this problem,
      we call an area from $i$-th kilometer to the $(i+1)$-th kilometer 
      a valley if $h_i<\min(h_{i-1},h_{i+1})$ and $0<i<n-1$. 
      The area before the first kilometer and the area after the $(n-2)$-th 
      are not considered as valleys, because $h_{-1}$ and ${h_n}$ are
      not defined.
\item A continuous segment is a unimodal interval if it has no valley in it
      except perhaps at either of its ends. 
      For example, if the query segment has heights $(1,2,3,4,3,4,5)$,
      then segments with heights $(1,2,3,4,3)$ and $(3,4,5)$ are unimodal 
      intervals, but that with height $(3,4,3,4)$ is not. 
\item Mr.\ Oshiro only builds his hotel on a unimodal interval. Thus, the 
      answer to the aformentioned query with heights $(1,2,3,4,3,4,5)$ is $5$.
\end{itemize}

Mysterious phenomena often occur in Celeste Mountain Range. 
Sometimes the height of a certain area will change. 
But don't worry, Mr.\ Oshiro will tell you the information just in time 
before he comes to you with more and more questions! 
